Making Sequential Programs Deterministic

### 2019-03-28 design.tex
removing array rules
Tweaks in 2.0

In a type system,
a \textit{type} stands for a set of values.  It abstracts or restricts the
set of possbile run-time values that an expression may evaluate to.
A programming language provides \emph{basetypes}, such as \<int>.
A \textit{type qualifier} on a \textit{type} adds additional constraints;
that is, it reduces the size of the set of values.
A type checker can verify the correctness of this \textit{type} with its dataflow analysis and subtyping rules.
In Java, a type qualifier is written as a type annotation with a leading \<@>, as in
\<@Positive int>.

@@

     $\infer[\textsc{ordernondet array}]{\wellformed{\kappa_e \ \beta_e \ \  \kappa_a []}}{\kappa_a : \|OrderNonDet/Det| & \kappa_e \sqsubseteq \kappa_a }$

    $\infer[\textsc{nondet array}]{\wellformed{\|NonDet| \ \beta_e \ \  \|NonDet| []}}{}$

@@

    $\infer[\textsc{arrays sort}]{\Gamma \vdash x : \|Det \ \beta \ Det[]| }{\Gamma \vdash x : \|Det \ \beta \ OrderNonDet[]| & \|Arrays.sort( \ x)|}$

>>>>

In a type system,
a \textit{type} represents a set of values.  It abstracts or restricts the
set of possbile run-time values that an expression may evaluate to.
A programming language provides \emph{basetypes}, such as \<int>.
A \textit{type qualifier} on a \textit{type} adds additional constraints;
that is, it reduces the size of the set of values.
In Java, a type qualifier is written as a type annotation (which has a leading \<@>), as in
\<@Positive int>.
A type checker can verify the correctness of a \textit{type} via subtyping
rules and dataflow analysis.

@@

%     $\infer[\textsc{ordernondet array}]{\wellformed{\kappa_e \ \beta_e \ \  \kappa_a []}}{\kappa_a : \|OrderNonDet/Det| & \kappa_e \sqsubseteq \kappa_a }$
%    
%    \bigskip

%    $\infer[\textsc{nondet array}]{\wellformed{\|NonDet| \ \beta_e \ \  \|NonDet| []}}{}$
%    
%    \bigskip

@@

%    \bigskip
%    
%    $\infer[\textsc{arrays sort}]{\Gamma \vdash x : \|Det \ \beta \ Det[]| }{\Gamma \vdash x : \|Det \ \beta \ OrderNonDet[]| & \|Arrays.sort( \ x)|}$
